Stay in shape! Homework exam II

### 2016-04-03 geometricAlgorithms/homeworkExam/2/homeworkExam.tex
generic approach
finished the algorithm

\subsection{Argue that all horizontal line segs are found}
All line segments are found because the binary search tree will
select as many as possible y based nodes and then ask the

\newpage
\subsection{Give psuedo code for the query algorithm}
\begin{algorithmic}[1]
	\Function{select}{$v$, $x \times [y:y']$}
		\If{$v$ is a leaf and $y < y_{val}(v) < y'$}
			\State
			\Return \Call{selectRange}{$subtree(v), x$}
		\EndIf
		\If{$y' < y_{val}(v)$}
		\State
		\Return \Call{select}{$c_{left}(v), x \times [y:y']$}
		\EndIf
		\If{$y > y_{val}(v)$}
		\State
		\Return \Call{select}{$c_{right}(v), x \times [y:y']$}
		\EndIf
		\State
		\Comment{If we get here it means we have a split node}
		\State
		\Return $\Call{reportLeft}{v, x\times y, c_{right}}\cup
		\Call{reportRight}{v,x\times y', c_{left}}$
	\EndFunction
	\Function{reportRight}{$v$, $x \times y$}
		\If{$isLeaf(v)$}
			\State
			\Return $\emptyset$
		\EndIf
		\If{$y \leq y_{val}(v)$}
		\State
		\Return $\Call{reportRight}{c_{left}(v), x \times y} \cup
		\Call{selectRange}{subtree(c_{right}(v)),x}$
		\EndIf
		\State
		\Return $\Call{reportRight}{c_{right}(v), x \times y}$
	\EndFunction
	\Function{reportLeft}{$v$, $x \times y$}
		\If{$isLeaf(v)$}
			\State
			\Return $\emptyset$
		\EndIf
		\If{$y > y_{val}(v)$}
		\State
		\Return $\Call{reportLeft}{c_{right}(v), x \times y} \cup
		\Call{selectRange}{subtree(c_{left}(v)),x}$
		\EndIf
		\State
		\Return $\Call{reportLeft}{c_{left}(v), x \times y}$
	\EndFunction
	\Function{selectRange}{$v$, $x$}
	\If{$v$ is a leaf}
		\State
		\Return $\emptyset$
	\EndIf
	\If{$x < x_{mid}(v)$}
		\State
		$r \gets $ starting at the leftmost endpoint keep
		returning all the intervals in $l_{left}(v)$ untill the
		intervals no longer contain $x$. (basically a takewhile
		operation in your favorite langauge).
		\State
		\Return $r \cup \Call{selectRange}{c_{left}(v),x}$
	\EndIf
	\State
	$r \gets $ starting at the rightmost endpoint keep
	returning all the intervals in $l_{right}(v)$ until the
	intervals no longer contain $x$.
	\State
	\Return $r \cup \Call{selectRange}{c_{right}(v),x}$
	\EndFunction
\end{algorithmic}
\subsection{Analyze the query time}

>>>>

\subsection{Argue that all horizontal line segs are found}
The outer tree will not start reporting untill it encounters a
split node. Then it will only report the inner tree if the
value of the nodes fall in the range of the query. So for
the $[y:y']$ part of the query the algorithm is correct.

The intervall tree for the $x$ part of the query will start
reporting as soon as it encounters a decision. However it
will only report the linesegements that intersect with $x$.

\subsection{Give psuedo code for the query algorithm}
\begin{algorithmic}[1]
	\Function{select}{$v$, $x \times [y:y']$}
		\If{$v$ is a leaf and $y < y_{val}(v) < y'$}
			\State
			\Return \Call{selectRange}{$subtree(v), x$}
		\EndIf
		\If{$y' < y_{val}(v)$}
		\State
		\Return \Call{select}{$c_{left}(v), x \times [y:y']$}
		\EndIf
		\If{$y > y_{val}(v)$}
		\State
		\Return \Call{select}{$c_{right}(v), x \times [y:y']$}
		\EndIf
		\State
		\Comment{If we get here it means we have a split node}
		\State
		\Return $\Call{reportLeft}{v, x\times y, c_{right}}\cup
		\Call{reportRight}{v,x\times y', c_{left}}$
	\EndFunction
	\algstore{tree}
\end{algorithmic}
\newpage
\begin{algorithmic}[1]
	\algrestore{tree}
	\Function{reportRight}{$v$, $x \times y$}
		\State
		$\phi \gets y \leq y_{val}(v)$
		\If{$isLeaf(v)$}
			\If{$\phi$}
				\State
				\Return $\Call{selectRange}{subtree(v),x}$
			\EndIf
			\State
			\Return $\emptyset$
		\EndIf
		\If{$\phi$}
		\State
		\Return $\Call{reportRight}{c_{left}(v), x \times y} \cup
		\Call{selectRange}{subtree(c_{right}(v)),x}$
		\EndIf
		\State
		\Return $\Call{reportRight}{c_{right}(v), x \times y}$
	\EndFunction
	\Function{reportLeft}{$v$, $x \times y$}
		\State
		$\phi \gets y > y_{val}(v)$
		\If{$isLeaf(v)$}
			\If{$\phi$}
				\State
				\Return $\Call{selectRange}{subtree(v),x}$
			\EndIf
			\State
			\Return $\emptyset$
		\EndIf
		\If{$\phi$}
		\State
		\Return $\Call{reportLeft}{c_{right}(v), x \times y} \cup
		\Call{selectRange}{subtree(c_{left}(v)),x}$
		\EndIf
		\State
		\Return $\Call{reportLeft}{c_{left}(v), x \times y}$
	\EndFunction
	\Function{selectRange}{$v$, $x$}
	\If{$v$ is a leaf}
		\State
		\Return $\emptyset$
	\EndIf
	\If{$x < x_{mid}(v)$}
		\State
		$r \gets $ starting at the leftmost endpoint keep
		returning all the intervals in $l_{left}(v)$ untill the
		intervals no longer contain $x$. (basically a takewhile
		operation in your favorite langauge).
		\State
		\Return $r \cup \Call{selectRange}{c_{left}(v),x}$
	\EndIf
	\State
	$r \gets $ starting at the rightmost endpoint keep
	returning all the intervals in $l_{right}(v)$ until the
	intervals no longer contain $x$.
	\State
	\Return $r \cup \Call{selectRange}{c_{right}(v),x}$
	\EndFunction
\end{algorithmic}
\subsection{Analyze the query time}
